Tracing the Stellar Halos of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam

### 2017-06-30 draft/paper1_rachel.tex
Section discussion

    Also according to this picture, the shape of the stellar halo should preserve
    information about the merging history and possibly even about the shape of the 
    dark matter halo. 
    Simulations show the shape of the stellar and dark matter halos are closely correlated (e.g. \citealt{Wu2014}) for slowly-rotating massive ETGs having undergone multiple 
    minor-mergers. The more elongated outer halo and the trend between the ellipticity profile and 
    stellar mass may reflect the orbital properties of infalling satellite. 
    In simulations, satellite orbits become more radial for more massive halos (e.g. \citealt{Murante2007, Wetzel2011, Jiang2015}. Satellites infalling along radial orbits may  help to form elongated  stellar halos. Hence, in principle, these results help explain the trend that we see. However, on contrast, simulation from \citet{Wu2014} predict that more massive 
    galaxies should have \emph{rounder} outskirts which is the opposite trend compared to HSC. This difference warrants further investigation.

    At larger scales, the distribution of satellites galaxies in massive halos is found to  be aligned with the major axis of the central galaxy \alexie{CHECK} (e.g. \citealt{Brainerd2005, 
    Yang2006b, NiedersteOstholt2010, HuangMandelbaum2016}). This alignement signal is found to be stronger for more massive \alexie{satellites???} galaxies (e.g. \citealt{Hirata2007}).
    The fact that more massive central galaxies have steeper ellipticity profiles 
    and become increasingly more elongated in the outskirt may arise because of such alignements. Moreover, the shape of the dark matter halo can be estimated by analyzing satellite distributions and weak lensing profiles (\citealt{ClampittJain2016}). 
    It is interesting to point out that the most recent measurement by 
    \citet{Shin2017} around SDSS clusters show a halo axis-ratio of ${\sim}0.55$, 
    which is only slightly more elongated than the stellar halo of galaxies in our 
    highest \mtot{} bin.

@@

    Recent hydrodynamic simulations of galaxy formation often separate stars in 
    galaxies into \textit{in situ} and \textit{ex situ} components. 
    In simulations, the \textit{in situ} component is often defined as the stars formed 
    in the halo of the ``main progenitor''.  
    The spatial distribution, kinematic, and stellar population properties of both 
    components are important theoretical predictions. Among various predictions,  the faction of  \textit{ex situ} stars and the scaling of the  ex situ fraction with galaxy mass is perhaps the  first aspect to test. However, on the observational side, there is no strightforward way to actually disentangle these two components for massive galaxies. Disk galaxies  are more easily decomposed into multiple components and recently, deep surveys of nearby disk galaxies have started to provide constraints on their stellar halos \alexie{NEED REFERENCE HERE}.

    For more massive ETGs,  results so far mainly depend on multi-component model fitting
    and image stacking analyses (e.g. \citealt{Huang2013a, DSouza2014, Spavone2017}).
    In this work, we propose that \mstar{} computed within different fixed physical apertures are worth exploring as  proxies of the  ex situ fraction. We propose to use the mass within 10 kpc (\minn{}) and 100 kpc (\mtot{}) as proxies for the \textit{in situ} component and for the total \mstar{}.

    On the left panel of Fig \ref{fig:discussion_1} we show the relation between \mtot{} and the fraction of mass between 10 and 100 kpc (as a proxy of the mass of the accreted component). We compare this with the  fraction of ex-situ stars predicted by the Illustris simulation 
    (\citealt{RodriguezGomez2016}).  We find that  our proxy for the accreted mass component correlates strongly with  \mtot{} and that this relation is surprisingly consistent with predictions from \citet{RodriguezGomez2016}.  Given the limitations of the Illustris simulation, and the imperfect nature of our proxy for the ex situ fraction proxy, the almost perfect agreement seen in Figure \ref{fig:discussion_1} may well be a coincidence.  However, it is encouraging to see that our simple proxy for the fraction of ex situ stars seems to match both the slope and the scatter of the predicted relation.  There exist other  hydrodynamic simulations that predict significantly different ex situ fractions compared to Illustris (e.g. 
    \citealt{Lackner2012, Qu2017}).  In future work, we will explore more detailed comparisons between our data and predictions from hydrodynamic simulations and we will  investigate to what degree simple aperture masses may be used to trace \textit{ex situ} fractions.

@@

   How well justified is our choice of  \minn{} as a proxy of the  in-situ component?  A full investigation is beyond the scope of this paper. Here we simply present a comparison  between our profiles and  a)  several estimates of the in-situ component and b) observations of high redshift massive galaxies that should be dominated by the  \textit{in situ} component.  In particular, we compare with:

@@

        \item The inner component of $z{\sim} 0$ ellipticals from the 2-D 
            decomposition of \citet{Huang2013a}. \citet{Huang2013b} showed 
            that this inner component is structurally similar to the compact ``red nuggets'' at  high-$z$. 
        \item The \textit{in situ} components of simulated central galaxies in 
            massive halos from \citet{Cooper2013} (the inner ${\sim} 5$ kpc is 
            quite uncertain due to the resolution).  
            These \mden{} profiles are generated using the particle tagging 
            method (see \citealt{Cooper2010})

@@

    We also compare with a uniquely massive BCG at high redshift: 
    a ${\sim} 10^{11.4} M_{\odot}$ BCG with a distinctive ``cD''-like envelope at 
    $z{\sim} 1.1$ (\citealt{Liu2013}).  This high redshift galaxy has a \mden{} profile that follows the median profile of our $11.6\leq$\logmtot{}$<11.8$ sample nicely inside 10-15 kpc, but becomes steeper in the outskirt. This suggest that the  inner ``core'' of massive BCGs are already in pace at $z{\sim} 1$ while the outer halo is still being assembled.

    These simple comparisons certainly support the idea that \minn{} mainly consists of 
    \textit{in situ} stars whereas mass at $\mathrm{R} > 15$-20 kpc is dominated by accreted 
    component.   Meanwhile, this comparison also shows that the \texttt{in situ} component may extend beyond 10 kpc\footnote{We convert these \mden{} profiles to the same 
    Chabrier IMF; but there are still differences in median \mstar{} and 
    details in the \m2l{} estimates}. Further comparisons with massive galaxies at high redshift and with hydrodynamicl simulations wil help understand which radius is optimal for probing the in situ mass.

>>>>

    Also according to this picture, the shape of the stellar halo should preserve
    information about the merging history and possibly even about the shape of the 
    dark matter halo. 
    Simulations show the shape of the stellar and dark matter halos are closely 
    correlated (e.g. \citealt{Wu2014}) for slowly-rotating massive ETGs having 
    undergone multiple minor-mergers.
    The more elongated outer halo and the trend between the ellipticity profile and 
    stellar mass may reflect the orbital properties of accreted satellite. 
    In simulations, satellite orbits become more radial for more massive halos 
    (e.g. \citealt{Murante2007, Wetzel2011, Jiang2015}. 
    Satellites infalling along radial orbits may help to form elongated stellar 
    halos. 
    Hence, in principle, these results help explain the trend that we see. 
    However, in contrast, simulation from \citet{Wu2014} predict that more massive 
    galaxies should have \emph{rounder} outskirts which is the opposite trend 
    compared to HSC. 
    This difference warrants further investigation.

    At larger scales, the distribution of satellites galaxies in massive halos is 
    found to be aligned with the major axis of the central galaxy 
    (e.g. \citealt{Brainerd2005, Yang2006b, NiedersteOstholt2010, 
    HuangMandelbaum2016}). 
    This alignment signal is found to be stronger for more massive galaxies 
    (e.g. \citealt{Hirata2007}).
    The fact that more massive central galaxies have steeper ellipticity profiles 
    and become increasingly more elongated in the outskirt may arise because of 
    such alignment. 
    Moreover, the shape of the dark matter halo can be estimated by analyzing 
    satellite distributions and weak lensing profiles (\citealt{ClampittJain2016}). 
    It is interesting to point out that the most recent measurement by 
    \citet{Shin2017} around SDSS clusters show a halo axis-ratio of ${\sim}0.55$, 
    which is only slightly more elongated than the stellar halo of galaxies in our 
    highest \mtot{} bin.

@@

    Recent hydrodynamic simulations of galaxy formation often separate stars in 
    galaxies into \textit{in situ} and \textit{ex situ} components. 
    In simulations, the \textit{in situ} component is often defined as the stars 
    formed in the halo of the ``main progenitor''.  
    The spatial distribution, kinematic, and stellar population properties of both 
    components are important theoretical predictions. 
    Among various predictions, the faction of \textit{ex situ} stars and the scaling 
    of the \textit{ex situ} fraction with stellar mass is perhaps the first aspect to 
    test. 
    However, on the observational side, there is no straightforward way to actually
    disentangle these two components for massive galaxies. 
    Disk galaxies are more easily decomposed into multiple components and recently, 
    deep surveys of nearby disk galaxies have started to provide constraints on 
    their stellar halos (e.g. \citealt{Courteau2011, Merritt2016, 
    Harmsen2017})\footnote{Although it is still not certain that all stellar halos
    around disk galaxies are made out of \textit{ex situ} stars.}.

    For more massive ETGs, results so far mainly depend on multi-component model 
    fitting and image stacking analyses (e.g. \citealt{Huang2013a, DSouza2014,
    Spavone2017}).
    In this work, we propose that \mstar{} computed within different fixed physical
    apertures are worth exploring as proxies of the \textit{ex situ} fraction. 
    We propose to use the mass within 10 kpc (\minn{}) and 100 kpc (\mtot{}) as 
    proxies for the \textit{in situ} component and for the total \mstar{}.

    On the left panel of Fig \ref{fig:discussion_1} we show the relation between 
    \mtot{} and the fraction of mass between 10 and 100 kpc (as a proxy of the mass of 
    the accreted component).
    We compare this with the fraction of \textit{ex-situ} stars predicted by the 
    Illustris simulation (\citealt{RodriguezGomez2016}).  
    We find that our proxy for the accreted mass component correlates strongly with  
    \mtot{} and that this relation is surprisingly consistent with predictions from
    \citet{RodriguezGomez2016}.  
    Given the limitations of the Illustris simulation, and the imperfect nature of 
    our \textit{ex situ} fraction proxy, the almost perfect agreement seen in 
    Figure \ref{fig:discussion_1} may well be a coincidence.  
    However, it is encouraging to see that our simple proxy for the fraction of 
    \textit{ex situ} stars seems to match both the slope and the scatter of the 
    predicted relation.  
    There exists other hydrodynamic simulations that predict significantly different 
    \textit{ex situ} fractions compared to Illustris (e.g. \citealt{Lackner2012, 
    Qu2017}). 
    In future work, we will explore more detailed comparisons between our data and
    predictions from hydrodynamic simulations and we will investigate to what degree 
    simple aperture masses may be used to trace \textit{ex situ} fractions.

@@

   How well justified is our choice of \minn{} as a proxy of the \textit{in-situ} 
   component?  
   A full investigation is beyond the scope of this paper. 
   Here we simply present comparisons between our profiles and  
   a) several estimates of the \textit{in-situ} component and 
   b) observations of high redshift massive galaxies that should be dominated by 
   the \textit{in situ} component.  
   In particular, we compare with:

@@

        \item The inner component of $z{\sim} 0$ ellipticals from the 2-D 
            decomposition of \citet{Huang2013a}. 
            \citet{Huang2013b} showed that this inner component is structurally 
            similar to the compact ``red nuggets'' at high-$z$.

        \item The \textit{in situ} components of simulated central galaxies in 
            massive halos from \citet{Cooper2013} (the inner ${\sim} 5$ kpc is 
            quite uncertain due to the resolution).  
            These \mden{} profiles are generated using the particle tagging 
            method (see \citealt{Cooper2010})

@@

    We also compare with a uniquely massive BCG at high redshift: 
    a ${\sim} 10^{11.4} M_{\odot}$ BCG with a distinctive ``cD''-like envelope at 
    $z{\sim} 1.1$ (\citealt{Liu2013}).  
    This high redshift galaxy has a \mden{} profile that follows the median \mden{} 
    profile of our $11.6\leq$\logmtot{}$<11.8$ sample nicely at $\mathrm{R} < 20$ 
    kpc, but the profile becomes much steeper in the outskirt. 
    This suggests that the inner ``core'' of massive BCGs are already in pace at 
    $z{\sim} 1$ while the outer halo is still being assembled.

    These simple comparisons certainly support the idea that \minn{} mainly consists 
    of \textit{in situ} stars whereas mass at $\mathrm{R} > 15$-20 kpc is dominated 
    by \textit{ex situ} component.  
    Meanwhile, this comparison also shows that the \texttt{in situ} component may 
    extend beyond 10 kpc\footnote{We convert these \mden{} profiles to the same 
    \citealt{Chabrier2003} IMF; but there are still differences in median \mstar{} 
    and details in the \m2l{} estimates}. 
    Further comparisons with massive galaxies at high redshift and with 
    hydrodynamical simulations will help understand which radius is optimal for 
    probing the \textit{in situ} mass.
